MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
empirical in progress

\begin{figure}[h]
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.65]{onelevel-tree.pdf}\\
    {\tiny Fig. 1: Search tree}
  \end{minipage}
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.4]{flat-trilevel-k=64-uqb=8.pdf}\\
    {\tiny Fig. 2: Regret vs number of samples}
  \end{minipage}
  \label{fig:mab-simple-regret}
\end{figure}
\begin{itemize}
\item For smaller numbers of
samples, $\frac 1 2$-greedy achieves the best
performance.
\item For larger numbers of samples, UCB$_{\sqrt{\cdot}}$
outperforms $\frac 1 2$-greedy. 
\item A combination of $\frac 1
2$-greedy  and UCB$_{\sqrt{\cdot}}$ dominates UCB over the
whole range.
\end{itemize}
\end{frame}

>>>>

\begin{figure}[h]
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.65]{onelevel-tree.pdf}\\
    {\scriptsize Fig. 1: Search tree}
  \end{minipage}
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.4]{flat-trilevel-k=64-uqb=8.pdf}\\
    {\scriptsize Fig. 2: Regret vs \# of samples (32 arms)}
  \end{minipage}
  \label{fig:mab-simple-regret}
\end{figure}
\begin{itemize}
\item For smaller numbers of
samples, $\frac 1 2$-greedy achieves the best
performance.
\item For larger numbers of samples, UCB$_{\sqrt{\cdot}}$
outperforms $\frac 1 2$-greedy. 
\item A combination of $\frac 1
2$-greedy  and UCB$_{\sqrt{\cdot}}$ dominates UCB over the
whole range.
\end{itemize}
\end{frame}

\begin{frame}{Monte Carlo tree search}

\begin{figure}[h]
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.45]{twolevel-tree.pdf}\\
    {\scriptsize Fig. 1: Search tree}
  \end{minipage}
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.4]{tree-identity-k=16-uqb=8.pdf}\\
    {\scriptsize Fig. 2: Regret vs \# of samples (16 switches)}
  \end{minipage}
  \label{fig:mab-simple-regret}
\end{figure}
\begin{itemize}
\item Either $\frac 1
2$-greedy+UCT or UCB$_{\sqrt{\cdot}}$+UCT
gives the lowest regret.
\item UCB$_{\sqrt{\cdot}}$+UCT dominates UCT everywhere
except for small numbers of instances. 
\item The advantage of both $\frac 1
2$-greedy+UCT and UCB$_{\sqrt{\cdot}}$+UCT grows with the number of
arms.
\end{itemize}
\end{frame}
